$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-08 paper/paper.tex
Draft on Orchard's work

@@

Based on contextual type theory \cite{Pientkaa, Pientka}, LINCX \cite{Georges2017} extends the linear logical framework LLF \cite{Cervesato1996} by internalising the notion of bindings and contexts.
The result is a meta-theory in which HOAS encodings with both linear and dependent types can be described.
The developer obtains for free an equational theory of substitution and decidable typechecking without having to encode context splits within the object language.

% Orchard
\cite{Orchard}

>>>>

Orchard et al. introduce Granule \cite{Orchard}, a fully-fledged language with graded modal types, linear types, indexed types and polymorphism.
Modalities include exact usages, security levels and intervals.
Grade terms allow for grade polymorphism and their resource algebra is based on a pre-ordered semiring with monotonic multiplication and partial addition.
They provide bidirectional typing rules, and show the type safety of their semantics.

@@

More generally, based on contextual type theory \cite{Pientkaa, Pientka}, LINCX \cite{Georges2017} extends the linear logical framework LLF \cite{Cervesato1996} by internalising the notion of bindings and contexts.
The result is a meta-theory in which HOAS encodings with both linear and dependent types can be described.
The developer obtains for free an equational theory of substitution and decidable typechecking without having to encode context splits within the object language.
